---
title: "Introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warning = F
)
# devtools::install_local(force = T)
```

```{r setup}
library(seascapeR)
```

## Get Seascape Dataset information

ERDDAP dataset info and date ranges for two available datasets: global_monthly and global_8day.

```{r}
s_mo <- get_seascape_info() # default: dataset = "global_monthly"
s_8d <- get_seascape_info("global_8day")
s_mo
s_8d

s_mo_dates <- get_date_rng(s_mo)
s_8d_dates <- get_date_rng(s_8d)
s_mo_dates
s_8d_dates
```

## Map Seascape image tiles

Plot a map of Seascape classes: 

```{r}
map_seascape_wms(s_mo_dates[2], ctr_lon = -81.3, ctr_lat = 24.5, ctr_dd = 10)
```

For now this is just using the `global_monthly` dataset. Note that the image tiles produces by the Web Map Server (WMS) do not contain the data, just tiled image. 

## Get Seascape data

Note that the monthly is a raster layer and 8day is raster stack for multiple dates.

```{r}
r_monthly <- get_seascape_data(ctr_lon = -81.3, ctr_lat = 24.5, ctr_dd = 10, dataset = "global_monthly", var = "CLASS", date_beg = "2020-11-01", date_end = "2020-12-01")
r_monthly

r_8day <- get_seascape_data(ctr_lon = -81.3, ctr_lat = 24.5, ctr_dd = 10, dataset = "global_8day", var = "CLASS", date_beg = "2020-11-01", date_end = "2020-12-01")
r_8day
```

## Map Seascape data

```{r}
map_seascape_raster(r_monthly)
```

For raster stacks, you need to subset to a raster layer:

```{r}
library(raster)
map_seascape_raster(raster(r_8day, 1))
```

And another raster layer:

```{r}
library(raster)
map_seascape_raster(raster(r_8day, 2))
```



