---
title: "Introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warning = F
)
# devtools::install_local(force = T)
# devtools::load_all()
```

```{r setup}
library(seascapeR)
```

## Get Seascape Dataset information

ERDDAP dataset info and date ranges for two available datasets: global_monthly and global_8day.

```{r}
# SeaScape dataset info
ss_gl_mo <- get_ss_info() # default: dataset = "global_monthly"
ss_gl_8d <- get_ss_info("global_8day")
ss_gl_mo
ss_gl_8d

# SeaScape date ranges
get_ss_dates(ss_gl_mo)
get_ss_dates(ss_gl_8d)
```

## Show Information on Seascape Classes

```{r}
# show dataset of Seascape Global Classes information
ss_gl_classes

# setup paths for plots generated in tables below
dir_svg  = here::here("inst/svg")
web_svg  = "../svg"

# show table for Seascape Class 1
tbl_ss_class(1, dir_svg, web_svg)

# show table for Seascape Class 15
tbl_ss_class(15, dir_svg, web_svg)

# show table for Seascape Class 33
tbl_ss_class(33, dir_svg, web_svg)
```

## Map Seascapes as image tiles

Get interactive map of Seascape classes: 

```{r}
map_ss_wms(ss_gl_mo)
```

Note that the image tiles produces by the Web Map Server (WMS) do not contain the data, just tiled image. 

## Define polygon for extraction of Seascapes

You can use any `sf` polygon object. This package has a couple helper functions to get polygons of interest, either a National Marine Sanctuary or a simple bounding box.

```{r}
# bounding box for Florida Keys area
lon = -81.3; lat = 24.5; w = 1.2
ply <- bbox_ply(lon - w, lat - w, lon + w, lat + w)
map_ss_wms(ss_gl_mo, ply)
```

```{r}
# setting variables and paths allows for caching data files
sanctuary = "fknms" # or see: ?get_url_ply
dir_data  = here::here("data_ss")
dir_ply   = glue::glue("{dir_data}/ply")
dir_ply

# get sanctuary polygon
ply <- get_url_ply(
  sanctuary = sanctuary, 
  dir_ply   = dir_ply)
```

```{r}
# show files
fs::dir_tree(dir_ply)
```

```{r}
# map image tiles with polygon
map_ss_wms(ss_gl_mo, ply)
```

## Get Seascape grids within polygon

```{r}
# variables and paths
ss_dataset  = "global_8day" # or "global_8day"
ss_var      = "CLASS"       # or "P"
date_beg    = "2020-01-01"
date_end    = "2020-06-01"
dir_grd     = glue::glue(
  "{dir_data}/{sanctuary}_{ss_dataset}")

ss_info <- get_ss_info(dataset = ss_dataset)

# get SeaScape grids from polyon for date range 
grds <- get_ss_grds(
  ss_info, ply, 
  ss_var    = ss_var, 
  date_beg  = date_beg, 
  date_end  = date_end,
  dir_tif   = dir_grd)

# show files
fs::dir_tree(dir_grd)
```

## Map Seascape grid with polygon

```{r}
# get first grid, a raster layer in the raster stack grds
grd <- raster::raster(grds, 1)

# map SeaScape grid
map_ss_grd(grd)
```

## Summarize Seascape grids into a time series table

```{r}
ts_csv = glue::glue(
  "{dir_data}/{sanctuary}_{ss_dataset}_{ss_var}.csv")

tbl <- sum_ss_grds_to_ts(grds, ts_csv = ts_csv)
tbl
```


## Plot Seascapes over time

```{r}
# plot SeaScape time series
plot_ss_ts(tbl)
```

